\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2020-06-26 redaction/submission_JEGeo/revision/referees/answers/Answer_referee1_Lise.tex

In italics, I report the Referee's comment. Into brackets in bold characters inserted into the referee's statement, my comment.

\textit{Using the notation of the authors, they are intreated
in identifying the share of the specific cost in the total transport cost. Namely,}
\begin{eqnarray*}
&& \frac{\frac{t_{is(k)}}{\tilde{p}_{ik}}}{\tau_{is(k)}-1 + \frac{t_{is(k)}}{\tilde{p}_{is(k)}}} \\
\text{or,} &&\frac{t_{is(k)}}{(\tau_{is(k)}-1)\tilde{p}_{is(k)} + t_{is(k)}}
\end{eqnarray*}

\textit{The way they approach the problem is that they assume that (a) $\tau_{ik} = \tau_i\tau_{k}$,
(b) $t_{ik} = t_i +t_k$, and (c) $t_k$ and $\tau_k$ are uniform across products within industry
s. After imposing these assumptions, they estimate the following specification}

\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)} -1+\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}} \right) + \epsilon_{ik} \label{eq:equation0}
\end{equation}

@@

\textbf{There is also a point here, about the degree of sectoral classification. In our paper, $k$ = 5 digit and $s(k)$ = 3 digit. He/she suggests that, in the estimated equation, $k$ = 10 digit and $s(k)$= 5 digit. Which means, having an estimated $\beta$ specific to the origin country-5-digit level. I need to have a refresher on this: What have we done finally? and why?}

XXX Say something about the fact that in the original US-custom data, the finest degree of sectoral classification is 8-digit, not 10? XXX

\subsubsection{What we do}

Our estimated equation is written as Equation (\ref{eq:equation0}) with $s$= 3 (or 4) digit and $k$=5 digit (based on Hummel's original dataset from 1974-2004). We thus exploit the variability of transport costs between countries and between 3-digit sectors (conditional on a year and a transport mode, air or vessel). To sum up our methodology:
\begin{itemize}
\item Estimating Equation \ref{eq:equation0} provides us with estimates of $\hat{t}_i$, $\hat{t}_{s(k)}$, $\hat{\tau}_i$, $\hat{\tau}_{s(k)}$.
\item We rebuild
\begin{eqnarray*}
\hat{t}_{is(k)} &= &\hat{t}_{i}+\hat{t}_{s(k)} \\
\hat{\tau}_{is(k)} &= & \hat{\tau}_{i}\times\hat{\tau}_{s(k)}
\end{eqnarray*}
\item We deduce the weighted average value of each component $\bar{t}$, $\bar{\tau}$ by year and transport mode, the weighting scheme being the relative value of the flows for each $i,s$ flow, as well as the median, the maximum and the minimum values.
\item With this in hand, we can (among other things) obtain the estimated share of additive costs in total transport costs for each $i,k$ flow:

@@

\subsection{To sum up: What remains to be done}

\begin{enumerate}
\item\label{bp:1} IV-First-stage equation on fas price at the 8-digit level, on recent years; then, run the estimation of the $\beta$ according to the referee's approach (considering $s(k)$ at the 3 digit level)
\item\label{bp:2} Run our original estimation method but with $k$ = 8-digit level on recent years for which we have the data. Also with $\widetilde{p}_{ik}$ instrumented as well? To be comparable with the point just above, yes. And compare with the $\beta$ obtained above (point \ref{bp:1}).
\item\label{bp:3} A table comparing the number of observations / countries / sectors 3D by year / transport mode when we do our empirical strategy vs the referee's strategy. Points (\ref{bp:1}, \ref{bp:2} and \ref{bp:3}) aim at providing answers to the general comment of the referee's Critique 1.
\item\label{bp:4} Comparison of the results of the $t,\tau,\beta$ obtained with our estimation method, for $k=5$ (what we have) and for $k=8$ (Referee's point 2), for recent years - No IV here?
\item\label{bp:5}IV-First-stage equation on fas price at the 5-digit level, for all years; then 2d-stage estimate of $t,\tau, \beta$ with our methodology; compare with our results obtained in the submitted version (Referee's point 1).
\end{enumerate}

\section{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

The referee is right in the sense that Census data do report the quantity of goods. However, this information is not mode-specific, which is incompatible with our empirical strategy of estimation transport costs conditional on the transport mode, similarly as in Hummels (2004). This explains why we cannot calculate the unit price as suggested by the referee.

At a more fundamental level, one might argue that considering the unit price as value/weight is relevant in our setting where we seek to identify transport costs. For instance, it makes sense that the shipment costs of cars do depend not only on the quantity of cars exported, but on the weight it makes, which is related to the volume it takes in the plane or the vessel. \textbf{Do we have evidence, even anecdotal, on this point? Is it an argument we want to make, See what Lashkaripour says about this point also.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogenity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. Also let $\widehat{p}_{ik} = Value/Quantity$
(unlike what the authors assume) denote standard definition of price}. As a consequence, making the link with the fas price we consider in the paper: $\widetilde{p}_{ik} = \widehat{p}_{ik} / \omega_{ik}$.

\textit{This paper is essentially estimating the following equation}:

\begin{equation*}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)} -1 +\frac{t_{i} + t_{s(k)}}{\widehat{p}_{ik}/\omega_{ik}} \right) + \epsilon_{ik}
\end{equation*}

\textit{instead of estimating}:

\begin{equation*}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)}-1 +\frac{t_{i} + t_{s(k)}}{\widehat{p}_{ik}} \right) + \epsilon_{ik}
\end{equation*}

\textit{There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity}

### 2020-06-29 redaction/submission_JEGeo/revision/referees/answers/Answer_referee1_Lise.tex

\begin{enumerate}
\item\label{bp:1} IV-First-stage equation on fas price at the 8-digit level, on recent years; then, run the estimation of the $\beta$ according to the referee's approach (considering $s(k)$ at the 3 digit level)
\item\label{bp:2} Run our original estimation method but with $k$ = 8-digit level on recent years for which we have the data. Also with $\widetilde{p}_{ik}$ instrumented as well? To be comparable with the point just above, yes. And compare with the $\beta$ obtained above (point \ref{bp:1}).
\item\label{bp:3} A table comparing the number of observations / countries / sectors 3D by year / transport mode when we do our empirical strategy vs the referee's strategy. Points (\ref{bp:1}, \ref{bp:2} and \ref{bp:3}) aim at providing answers to the general comment of the referee's Critique 1.
\item\label{bp:4} Comparison of the results of the $t,\tau,\beta$ obtained with our estimation method, for $k=5$ (what we have) and for $k=8$ (Referee's point 2), for recent years - No IV here?
\item\label{bp:5}IV-First-stage equation on fas price at the 5-digit level, for all years; then 2d-stage estimate of $t,\tau, \beta$ with our methodology; compare with our results obtained in the submitted version (Referee's point 1).
\end{enumerate}

\section{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

The referee is right in the sense that Census data do report the quantity of goods. However, this information is not mode-specific, which is incompatible with our empirical strategy of estimation transport costs conditional on the transport mode, similarly as in Hummels (2004). This explains why we cannot calculate the unit price as suggested by the referee. \textbf{We make this point clear in Footnote XXX}

\textbf{EN MEME TEMPS: Si on écarte de l'analyse les flux qui sont passés à la fois par bateau et par air, en ne gardant que les flux qui ont fait l'un ou l'autre, ne peut-on pas se dire que la quantité (pas mode-spécifique) a totalement voyage par vessel (si le flux indique qqch pour ves-val) ou par avion (s'il indique qqch pour air-val)? Et à ce moment là, on peut répondre ``vraiment'' à sa critique?}

@@

\begin{equation*}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)} -1 +\frac{t_{i} + t_{s(k)}}{\widehat{p}_{ik}/\omega_{ik}} \right) + \epsilon_{ik}
\end{equation*}

\textit{instead of estimating}:

\begin{equation*}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i} \times \tau_{s(k)}-1 +\frac{t_{i} + t_{s(k)}}{\widehat{p}_{ik}} \right) + \epsilon_{ik}
\end{equation*}

\textit{There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

We thank the referee for pointing out this potential source of bias in our estimates. If we cannot follow the referee's advice be replacing weight by quantity for data availability reasons, we can address his/her concern regarding this as source of endogeneity bias by instrumenting the fas price. \textbf{il ne faudrait pas dans ce cas mettre de lagged prices, sinon on reintroduit du bruit. Non?}

\section{Critique 3: Big Picture Implications}

\textit{My third critique concerns the lack of an exciting punchline. The fact that
composition effects have not countervailed the reduction in pure transport costs
(at least not as much as previously believed) is an interesting but minor observation.
Does this observation revise our understanding of say the gains from
trade? Does it shed new light on a puzzle many people are thinking about?
One crude suggestion is to see how the reduction in the industry-specific cost
terms is related to the industry-level trade elasticities. If the composition effects
favor low-elasticity industries, the findings in the paper may have first-order
implications for the gains from trade.
Another suggestion is to dig deeper into the relative rate at which additive
and multiplicative transport costs have declined over time. Since additive transport
costs favor rich (high-quality exporting) countries, the disproportionally
greater reduction in additive costs can perhaps explain the rise of low-income
exporter as documented by Hanson (2012, JEP).}

\textbf{Comments about that}

\paragraph{Piste 1} Consider his/her first suggestion. What is the idea? First, the link between gains from trade and trade-elasticity. Am I correct in saying that gains from trade are higher when trade is about low-elasticity goods? The idea being, if national goods are low substitutes, then here are larger gains from trading them. So, if composition effects (trade shifts between sectors) favor low-elasticity sectors, then one might expect high gains from trade. Hummels: trade composition effects matter as they partially offset the reduction in pure transport costs for both air and vessel. Over time, tendency to trade goods more costly to export everything else equal. So, if the referee's assertion is right (trade composition effects favor low-elasticity sectors), then increasing gains from trade. But, we disagree with Hummel's findings (his way of measuring things is inappropriate) and find that trade composition effects do not matter much, at least for air. Meaning that gains from trade are purely due to reduction in transport costs within sector, but not from switch towards low-elasticity sectors. Identify one source of gains from trade, not two.

What to do with this?

\paragraph{Piste 2}

### 2020-06-29 redaction/submission_JEGeo/revision/referees/answers/Answer_referee1_Lise.tex

\textbf{Comments about that}

\paragraph{Piste 1} Consider his/her first suggestion. What is the idea? First, the link between gains from trade and trade-elasticity. Am I correct in saying that gains from trade are higher when trade is about low-elasticity goods? The idea being, if national goods are low substitutes, then here are larger gains from trading them. So, if composition effects (trade shifts between sectors) favor low-elasticity sectors, then one might expect high gains from trade. Hummels: trade composition effects matter as they partially offset the reduction in pure transport costs for both air and vessel. Over time, tendency to trade goods more costly to export everything else equal. So, if the referee's assertion is right (trade composition effects favor low-elasticity sectors), then increasing gains from trade. But, we disagree with Hummel's findings (his way of measuring things is inappropriate) and find that trade composition effects do not matter much, at least for air. Meaning that gains from trade are purely due to reduction in transport costs within sector, but not from switch towards low-elasticity sectors. Identify one source of gains from trade, not two.

What to do with this?

\paragraph{Piste 2} What is at stake? Show that how $\beta$ = the relative share of additive costs has evolved over time. Good idea as this is really what differentiates us from Hummels, model a varying $\beta$ over time. Specifically, how methodology lets the $\beta$ vary over the three time-sector-partner country dimension. Show how $\beta$ varies over time everything else equal? Hopefully, goes in the referee's direction (decreases over time) with possibly a role in the understanding in the ``big picture'' of trade patterns?

### 2020-06-29 redaction/submission_JEGeo/revision/referees/answers/Answer_referee1_Lise.tex

\textit{where $d$ denotes the US district of entry and $k$ denotes an HS10 product. The
identification of $\beta_{ik}$, in this case, would rely on the across HS10 product and
district-of-entry variation in $f_{ik}$ and $p_{ik}$. Estimating the above equation would
obviously require that the authors do not aggregate up the raw Census data
across all districts and all 10-digit products pertaining to the same 5-digit category.}

\textit{The first advantage of this so-called Hummel's Approach is that the above
regression can be estimated separately for various country-industry pairs, without
imposing Assumptions (a) and (b), outlined above.}

\textbf{I report here the referee's footnote: Should we deal with this? If he/she is not convinced because small sub-sample, do it on a much larger sample? This would better convince him that the separability assumption is not an issue.}: \textit{The authors do check the robustness of their results w.r.t. the separability assumption, but this only done for a small sub-sample.}

\textbf{GD20200629 Ce n’est pas un si petit sample que cela (surtout en terme de valeurs -- comparer avec le sample sur lequel on peut faire sa propre méthode)}

@@

\textbf{There is also a point here, about the degree of sectoral classification. In our paper, $k$ = 5 digit and $s(k)$ = 3 digit. He/she suggests that, in the estimated equation, $k$ = 10 digit and $s(k)$= 5 digit. Which means, having an estimated $\beta$ specific to the origin country-5-digit level. I need to have a refresher on this: What have we done finally? and why?}

\textbf{Dans revision_estim_TC_referee1_nonlinear.do, il me semble qu’on fait 8 et 3. on peut effectivement faire sa méthode en 10 et 3 (ou 10 et 5)}

@@

The estimation strategy suggested by the referee starts from Equation (\ref{eq:Hummels}) linking transport costs and unit prices as assumed in Hummels (2007). As shown in Subsection (\ref{ssec:interpret_beta}), the elasticity of transport costs to unit prices $\beta_{ik}$ in Equation (\ref{eq:Hummels}), also corresponds to the share of additive costs in total transport costs. The share of aditive costs can hence be encovered by regressing transport costs on unit (ie, fas) prices. Specifically, the referee suggests to run the estimation based on Equation (\ref{eq:estimation_ref1}).

Precisely, by year and transport mode, this implies running the estimation for each country of origin $i$ and each sector $s(k)$ = 3 digit sector (\textbf{why 3-digit? and not 5 as suggested by the referee?}, exploiting the variability between sub-sectors at the 8 digit level ($k$) and between ports of entry in the US ($d$).

\subsubsection{Strategy of answer}

\paragraph{a) The advantages are not as important as suggested by the referee}
\begin{itemize}
\item[Advantage 1]: One is not compelled to assume separability between the country-component and the product-component of transport costs.
\item[$\Rightarrow$] Answer can be in 2 parts: 1) This is not a strong assumption - better convince him/her: Run the robustness to the separability assumption on a larger sample and show that the estimated $\beta$ is not that different between the two methods. 2) Compare the estimated $\beta$ between our original method and the referee's one. \
\textbf{Where are the results comparing the estimates of the $\beta$, in value? I don't find these results anymore...}
\textbf{GD20200629 -- Voir le plan des do. Pour comparaison scatter_chronology_baselinesamplereferee1_referee1.pdf (sur le même sample))}

\item[Advantage 2]: There is a handful of instruments (HS-8 product-specific tariff rates or lagged prices) to instrument fas prices
\item[$\Rightarrow$] Answer: When we instrument fas prices at the 5-digit level using tax duties (still using our own methodology), we do not obtain much different results. \textbf{But he/she suggests to do it on HS-8 fas prices, not 5-digit prices, and to imply his estimated equation. Have we done that?}
\textbf{GD20200629 Cela ne semble pas vrai. Il y a quelque années en HS8, plus en HS6. Mais pas sur toute la durée}
\item[Advantage 3]: A more transparent comparison with Hummel (2007): How to answer to this point? Re-read the paper to see if we are clear enough?
\textbf{GD20200629 changer la manière dont on présente en mettant les beta en avant ?}
\end{itemize}

@@

\paragraph{b) The costs are high}
\begin{itemize}
\item[Concern 1] The suggested estimation strategy implies having much less data to exploit, for two reasons.
\begin{enumerate}
\item Information about the port of entry are only available in the recent years (\textbf{since when? why? before, we rely on Hummel's data set, but we could buy the original US custom data for 1974-2004? Or even in those dataset it does not exist?}). In our view, the historical coverage is interesting per se, as it provides useful insights about how transport costs have evolved over time, and most importantly how the specific values of the additive and ad-valorem transport costs components have evolved over time. Eliminating this dimension of the paper would be detrimental to its value-added.
\item As underlined before, the method is run country by country, and 3-digit sector by 3-digit sector, exploiting the variability within each country-3d sector across 8-d sub-sectors and ports of entry. Yet, it appears that for many couples (country, 3-digit sector), there is too few variability across sub-sectors (even at the HS-6 digit classification) or ports en entry given the number of fixed effects included in the regression, such that estimation can not be run. This can be seen comparing the number of observations by year/ transport mode with our method / with the referee's method reported in Table XXX \textbf{TO DO}. Put it differently, this methodology discards countries which export a limited range of goods to the US and/or which arrive in the USA through the same ports of entry. In this respect, the induced selection bias reduces the general scope of the transport costs estimates.

\textbf{GD20200629 Les données commencent en 1989. On va demander}

@@

    As a direct consequence of this, for things to be comparable across methods, we re-run our estimation strategy on the same sample of observations as the one used in the referee's method.

    \end{enumerate}
\item[Concern 2] The suggested estimation method implicitly assumes that transport costs of say, tissues, have nothing in common whether those goods comes from France or from Bangladesh; or that transport costs that apply to imported goods from France have no common component across sectors; in both cases, one might view this as a disputable assumption. By contrast, we suppose that transport costs are sector-country specific. \textbf{FAIRE REFERENCE A DES PAPIERS EN TRADE QUI ONT DES TRADE COSTS Pays-spécifique?}
\item[Concern 3] The suggested estimation method does not allow to recover the values of each component of transport costs separately, but only the relative shares; while our methodology drives an estimate for each component ($\tau$, $t$) from which we can deduce the relative share of each. In this respect, we gain in generality. \textbf{DEEPEN this for the Big picture part}.
\textbf{GD20200629 Je ne comprends pas. Si on a les parts et les coûts totaux, on peut reconstruire $\tau$, $t$}
\item[Concern 4] The suggested method features less accuracy in the estimation of the $\beta$. Considering the value of the $\beta$ by itself, there is no criteria to discriminate between the value estimated with our method and the one obtained with the suggested method (when, of course, run on the same sample). Things are more clear-cut in terms of accuracy of the estimation. Specifically, our method yields a more precise estimation of the $\beta$ than the referee's method. To develop on this, for each year and transport mode:
    \begin{itemize}
    \item With the referee's method, we estimate one value for the share of additive component $beta$ at the $i,s$ level denoted $\hat{\beta}^{ref}_{is(k)}$ associated with a standard deviation $SD_{is}$. From this, we can deduce the 5- 95\% threshold values through:
        $$\hat{\beta}_{is}^{min,ref} = \hat{\beta}^{ref}_{is(k)} - 1.96 SD_{is},\quad \hat{\beta}_{is}^{max,ref} = \hat{\beta}^{ref}_{is(k)} + 1.96 SD_{is}$$

### 2020-07-02 redaction/submission_JEGeo/revision/referees/answers/topo_first_stage.tex
changement réponse référé 1

Denoting $i$ the origin country, $k$ the product at the 8/5 digit level, and reasoning on a yearly basis, if we assume that the fas price $\widetilde{p}_{ik}$ decomposes in two components, say $\bar{p}_{ik}$ the ``firm-specific'' price (related to its cost and pricing strategy) and $\tau^d_{ik}$ the tax duty (out of the firm's hands) according to :

@@

\noindent with $s(k)$ the 3-digit classification (the disaggregation level for tax duties in the database) as a function of the HS8 (or 5 digit) product classification

@@

If this reasoning is correct,
\begin{itemize}
\item we should take as predicted value only the predicted price WITHOUT the fixed effects:
$$\widehat{\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}} = \widehat{\alpha}\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $$
\item and we should expect a value of the coefficient $\widehat{\alpha}$ between $\Delta \log \widetilde{p}_{ikt}$ and $\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $ between $-1$ and $0$, depending on the degree of ``pricing-to-market'' of firms.
    \begin{itemize}
    \item[-] $\alpha = 0$ corresponds to the case where the firm does not adjust its fas price to the change in tax duty, that would cancel out the influence of the tax duty change on the price paid by the US consumers; this rather corresponds to small firms which do not have enough market power to manipulate their prices following changes in international competition;
    \item[-] $\alpha <0$ corresponds to the degree of``pricing-to-market'' as the firm offsets the impact of the tax change of the price paid by the final consumer by adjusting her producer price in the opposite direction of the tax change,
    \item[-] with $\alpha = -1$ being the extreme case of ``full PTM'' where the firm fully compensates the tax duty change. As shown by Berman, Martin, Mayer (REStats 2012), this is more likely larger firms.
    \end{itemize}
\end{itemize}

@@

\begin{eqnarray*}
\widehat{\widetilde{p}}_{ikt} = \widetilde{p}_{ikt-1}+ \widehat{\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}}
\end{eqnarray*}

with $\widehat{\widetilde{p}}_{ikt}$ the instrumented fas price at time $t$, for product $k$ from country $i$; $\widetilde{p}_{ikt-1}$ the observed lagged fas price for the same $i,k$ couple; and $ \widehat{\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}}$ the predicted growth rate of the fas price based on duty changes.

>>>>

Denoting $i$ the origin country, $k$ the product at the 5 digit level, and reasoning on a yearly basis, if we assume that the fas price $\widetilde{p}_{ik}$ decomposes in two components, say $\bar{p}_{ik}$ the ``firm-specific'' price (related to its cost and pricing strategy) and $\tau^d_{ik}$ the tax duty (out of the firm's hands) according to :

@@

\noindent with $s(k)$ the 3-digit classification as a function of the 5-digit product classification.

@@

If this reasoning is correct,
\begin{itemize}
\item we should take as predicted value only the predicted price WITHOUT the fixed effects:
$$\left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV} = \widehat{\alpha}\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $$
\item and we should expect a value of the coefficient $\widehat{\alpha}$ between $\Delta \log \widetilde{p}_{ikt}$ and $\frac{\Delta \tau^d_{is(k)t}}{1+\tau_{is(k)t-1}^d} $ between $-1$ and $0$, depending on the degree of ``pricing-to-market'' of firms.
    \begin{itemize}
    \item[-] $\alpha = 0$ corresponds to the case where the firm does not adjust its fas price to the change in tax duty, that would cancel out the influence of the tax duty change on the price paid by the US consumers; this rather corresponds to small firms which do not have enough market power to manipulate their prices following changes in international competition;
    \item[-] $\alpha <0$ corresponds to the degree of``pricing-to-market'' as the firm offsets the impact of the tax change of the price paid by the final consumer by adjusting her producer price in the opposite direction of the tax change,
    \item[-] with $\alpha = -1$ being the extreme case of ``full PTM'' where the firm fully compensates the tax duty change. As shown by Berman, Martin, Mayer (REStats 2012), this is more likely larger firms.
    \end{itemize}
\end{itemize}

@@

\begin{eqnarray*}
\widehat{\widetilde{p}}_{ikt} = \widetilde{p}_{ikt-1}\left[1 + \left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV}\right]
\end{eqnarray*}

with $\widehat{\widetilde{p}}_{ikt}$ the instrumented fas price at time $t$, for product $k$ from country $i$; $\widetilde{p}_{ikt-1}$ the observed lagged fas price for the same $i,k$ couple; and $ \left(\frac{\Delta \widetilde{p}_{ikt}}{\widetilde{p}_{ikt-1}}\right)^{IV}$ the predicted growth rate of the fas price based on duty changes.
